---
title: "Banner Table Template"
#author: "Samantha Goldstein"
#date: "1/29/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, echo=FALSE}
library(haven)
library(tidyverse)
library(htmlTable)
library(htmlwidgets)
library(expss)
library(survey)
library(magrittr)
library(labelled)
library(questionr)
library(readxl)
library(kableExtra)
library(weights)
library(conflicted)

conflict_prefer("filter", "dplyr")
conflict_prefer("select", "dplyr")

survey <- read_sav("df.sav")

```

```{r, include=FALSE, echo=FALSE}

## Clean and recode data
survey = survey %>% select(c(-uuid,-psid))

survey = survey %>% mutate(age5 = 2020 - Q58)
survey = survey %>% mutate(agebreak = case_when(age5 %in% c(17:22)~1,
                                                age5 %in% c(23:25)~2,
                                                age5 %in% c(26:29)~3,
                                                age5 %in% c(30:36)~4))

survey = survey %>% mutate(pid_lean = case_when(Q53==1~1, # Rep
                                                Q53==2~2, # Dem
                                                Q53==3 & Q54==3~3, # Indep
                                                Q53==3 & Q54==1~4, #Lean Rep
                                                Q53==3 & Q54==2~5 #Lean Dem
                                                ))


survey = survey %>% mutate(educbreak = case_when(Q56%in%c(1:3)~1, # HS or less
                                           Q56%in%c(4:5)~2, # Some college
                                           Q56%in%c(6:9)~3)) # College or more


survey = survey %>% mutate(race_and_educ = case_when(
                               Q59==1 & Q56%in%c(1:4) ~ 1, #White non-college
                               Q59==1 & Q56%in%c(5:9) ~ 2, #White college
                               Q59==2 & Q56%in%c(1:4) ~ 3, #Black non-college
                               Q59==2 & Q56%in%c(5:9)~ 4, #Black college
                               Q59==3 & Q56%in%c(1:4)~ 5, #Asian non-college
                               Q59==3 & Q56%in%c(5:9)~ 6, #Asian college
                               Q59==4 & Q56%in%c(1:4)~ 7, #Hispanic non-college
                               Q59==4 & Q56%in%c(5:9)~ 8)) #Hispanic college

survey = apply_labels(survey, agebreak = c("18-22"=1,
                                 "23-25"=2,
                                 "26-29"=3,
                                 "30-35"=4),
                      educbreak = "Education", 
                      educbreak = c("HS or less"=1,
                                    "Some college"=2,
                                    "College or more"=3),
                      pid_lean = "Party ID with Leans",
                      pid_lean = c("Republican"=1, "Democrat"=2, "Independent"=3, "Lean Republican"=4, "Lean Democrat"=5),
                      race_and_educ = "Race & Education", 
                      race_and_educ = c("White non-college"=1,"White college"=2, "Black non-college"=3, "Black college"=4, "Asian non-college"=5,"Asian college"=6, "Hispanic non-college"=7, "Hispanic college"=8),
                      race = "Race",
                      race = c("White"=1,"Black"=2,"Hispanic"=3, "Other"=4))

```

```{r, include=FALSE, echo=FALSE}
banner_tab_1 <- function(question) {
    cro_cpct(cell_vars = survey[[question]],
            col_vars = list(total(), 
                            survey$Q53,
                            survey$Q64,
                            survey$race),
            weight = survey$weight,
            total_row_position = "none",
            total_label = "Total (%)") %>%
      drop_empty_columns() %>%
      drop_empty_rows()
}

banner_tab_2 <- function(question) {
    cro_cpct(cell_vars = survey[[question]],
            col_vars = list(total(), 
                            survey$educbreak,
                            survey$agebreak),
            weight = survey$weight,
            total_row_position = "none",
            total_label = "Total (%)") %>%
      drop_empty_columns() %>%
      drop_empty_rows()
  }
```
Q1. Some people are registered to vote and others are not. Are you registered to vote in the precinct or ward where you now live, or aren't you?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q1")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Yes, Registered to Vote","No, Not Registered to Vote","Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q1")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Yes, Registered to Vote","No, Not Registered to Vote","Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q2. What are the chances that you will vote in the November 2020 general election for president, Congress, and other offices—are you absolutely certain to vote, very likely to vote, are the chances 50-50, or don't you think you will vote?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Absolutely certain","Very likely", "50-50", "Will not vote", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Absolutely certain","Very likely", "50-50", "Will not vote", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q3. Over the past year, do you feel the economy has gotten better, gotten worse, or stayed about the same?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q3")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Gotten better","Gotten worse", "Stayed the same", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q3")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Gotten better","Gotten worse", "Stayed the same", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q4.  Some people seem to follow what's going on in politics most of the time, whether there's an election going on or not. Others aren't that interested. Would you say you follow what's going on in politics most of the time, some of the time, only now and then, or hardly at all?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q4")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Most of the time","Some of the time", "Only now and then", "Hardly at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q4")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Most of the time","Some of the time", "Only now and then", "Hardly at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q5. Now, thinking about things in the country, do you think things in the United States are generally going in the right direction, or do you feel things have gotten off on the wrong track?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q5")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Right direction","Wrong track", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q5")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Right direction","Wrong track", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q6. Overall, do you approve or disapprove of the way Donald Trump is handling his job as President? 
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q6")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Approve","Disapprove", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q6")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Approve","Disapprove", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Below are a list of countries that have been in the news recently. For each one, please tell me whether you have a favorable or unfavorable impression of that country
\newline
\newline
Q20. Do you have a favorable or unfavorable impression of Australia?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q20")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q20")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q21. Do you have a favorable or unfavorable impression of China?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q21")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q21")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q22. Do you have a favorable or unfavorable impression of Russia?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q22")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q22")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q24. Do you have a favorable or unfavorable impression of Iran?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q24")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q24")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q25. Do you have a favorable or unfavorable impression of England?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q25")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q25")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Strongly favorable","Somewhat favorable", "Somewhat unfavorable", "unfavorable", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Below are a list of words and phrases that people use to describe different groups of people in American society. For each one, please indicate whether you think that the word describes immigrants very well, pretty well, not too well, or not well at all.
\newline
\newline
Q26. Dishonest
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q26_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q26_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q27. Powerful
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q27_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q27_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q28. Friendly
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q28_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q28_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q29. Serious
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q29_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q29_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q30. Kind
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q30_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q30_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q31. Intelligent
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q31_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q31_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q32. Innovative
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q32_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q32_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q33. Dominating
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q33_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q33_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q34. Warm
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q34_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q34_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q35. Privileged
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q35_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q35_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q36. Selfish
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q36_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q36_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q37. Sneaky
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q37_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q37_2")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very well","Pretty well", "Not too well", "Not well at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
How worried are you about the following aspects of your life – very worried, somewhat worried, not too worried, not worried at all? 
\newline
\newline
Q38. My financial situation
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q38")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q38")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q39. My health and fitness
```{r, echo=FALSE, format="latex", format="latex"}
banner_tab_1("Q39")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q39")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q40. My social life
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q40")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q40")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q41. My career
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q41")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q41")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q42. My romantic life
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q42")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q42")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q43. My religious or spiritual life
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q43")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q43")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Very worried","Somewhat worried", "Not too worried", "Not too worried at all", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q44. Which description comes closest to how you would describe yourself?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q44")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("I am always optimistic and rarely worry","I worry at times, but don't usually sweat the little things", "I am neither positive nor do I worry", "I worry more than I would like to, even when I should not", " I worry a lot and experience anxiety")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q44")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("I am always optimistic and rarely worry","I worry at times, but don't usually sweat the little things", "I am neither positive nor do I worry", "I worry more than I would like to, even when I should not", " I worry a lot and experience anxiety")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q45. And, which description comes closest to how you would describe your social life?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q45")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("I am lonely and do not have a good network of friends","I have a few friends, but am not very connected to them", "I have enough good friends, and am ok with my social life", "I have a good social life, and lots of friends", "I have a wonderful social life; I have many good friends and see them often")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q45")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("I am lonely and do not have a good network of friends","I have a few friends, but am not very connected to them", "I have enough good friends, and am ok with my social life", "I have a good social life, and lots of friends", "I have a wonderful social life; I have many good friends and see them often")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q46. How often do you use social media?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q46")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Multiple times a day","Once a day", "A couple times a week","Once a week", "Once a month", "Never")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q46")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("Multiple times a day","Once a day", "A couple times a week","Once a week", "Once a month", "Never")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q47. Which of the following best describes your use of social media?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q47")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("I use social media actively. I post my thoughts and share my emotions", "I use social media passively. I like and share other people’s posts")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q47")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("I use social media actively. I post my thoughts and share my emotions", "I use social media passively. I like and share other people’s posts")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q48 Split A. Which of the following statements come closest to your view, even if neither is exactly right?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q48A")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("World events are the result of unpredictable events", "There is a group of powerful people pulling the strings in secret", "Both", "Neither", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q48A")%>%
      subset(select = -row_labels) %>%
      as.data.frame(row.names=c("World events are the result of unpredictable events", "There is a group of powerful people pulling the strings in secret", "Both", "Neither", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q55. If the Democratic primary for president were being held today, for whom would you vote? 
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q55")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Joe Biden","Mike Bloomberg","Pete Buttigieg","Tulsi Gabbard","Amy Klobuchar","Deval Patrick","Bernie Sanders","Tom Steyer","Elizabeth Warren","Andrew Yang","Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q55")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Joe Biden","Mike Bloomberg","Pete Buttigieg","Tulsi Gabbard","Amy Klobuchar","Deval Patrick","Bernie Sanders","Tom Steyer","Elizabeth Warren","Andrew Yang","Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q56. What is the highest level of education you completed?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q56")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Elementary school only",
"Some high school / Did not finish",
"Completed high school",
"Some college but didn't finish",
"Two year college degree / A.A. / A.S.",
"Four year college degree / B.A. / B.S.",
"Some graduate work",
"Completed masters or professional degree",
"Advanced graduate work or Ph.D",
"Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q56")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Elementary school only",
"Some high school / Did not finish",
"Completed high school",
"Some college but didn't finish",
"Two year college degree / A.A. / A.S.",
"Four year college degree / B.A. / B.S.",
"Some graduate work",
"Completed masters or professional degree",
"Advanced graduate work or Ph.D",
"Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q57. Are you currently married, widowed, divorced, separated, or have you never been married?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q57")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Married", "Widowed","Divorced","Separated","Never been married", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q57")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Married", "Widowed","Divorced","Separated","Never been married", "Don't know"))%>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q59. Would you describe yourself as?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q59")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("White", "African American or Black","Asian, or South Asian or Pacific Islander","Hispanic or Latino","Native American or American Indian", "Other (specify)", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q59")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("White", "African American or Black","Asian, or South Asian or Pacific Islander","Hispanic or Latino","Native American or American Indian", "Other (specify)", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q60. Are you of Hispanic or Latino origin or background?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q60") %>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Yes", "No")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q60")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Yes", "No")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q61. What is your current religion, if any?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q61")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Protestant",
"Roman Catholic (Catholic)",
"Jewish (Judaism)",
"Muslim (Islam)",
"Buddhist",
"Hindu",
"Atheist (do not believe in God)",
"Agnostic (not sure if there is a God)",
"Something else",
"Or nothing in particular",
"Don't Know/Refused")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q61")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Protestant",
"Roman Catholic (Catholic)",
"Jewish (Judaism)",
"Muslim (Islam)",
"Buddhist",
"Hindu",
"Atheist (do not believe in God)",
"Agnostic (not sure if there is a God)",
"Something else",
"Or nothing in particular",
"Don't Know/Refused")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q62. Would you consider yourself a born-again or evangelical Christian, or not?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q62")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Yes", "No", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q62")%>%
      subset(select = -row_labels)   %>%
      as.data.frame(row.names=c("Yes", "No", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Q63. Aside from weddings and funerals, how often do you attend religious services?
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q63")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Once a week or more","Once or twice a month", "A few times a year", "Seldom", "Never", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q63")%>%
      subset(select = -row_labels)   %>%
      as.data.frame(row.names=c("Once a week or more","Once or twice a month", "A few times a year", "Seldom", "Never", "Don't know")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Party ID with Leans
```{r, echo=FALSE, format="latex"}
banner_tab_1("pid_lean")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Republican","Democrat", "Independent", "Lean Republican", "Lean Democrat")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("pid_lean")%>%
      subset(select = -row_labels)   %>%
      as.data.frame(row.names=c("Republican","Democrat", "Independent", "Lean Republican", "Lean Democrat")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
\newpage
Gender
```{r, echo=FALSE, format="latex"}
banner_tab_1("Q64")%>%
      subset(select = -row_labels)  %>%
      as.data.frame(row.names=c("Male", "Female")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "Republican", "Democrat",  "Independent", "Male", "Female", "White", "Black", "Hispanic", "Other")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left", fixed_thead = T)

banner_tab_2("Q64")%>%
      subset(select = -row_labels)   %>%
      as.data.frame(row.names=c("Male", "Female")) %>%
      kable(booktabs=TRUE, digits = 2, col.names = c("Total", "HS or Less", "Some College",  "College or More", "18-22", "23-25", "26-29","30-35")) %>%
      kable_styling(latex_options = c("scale_down"),
                    position="left",  fixed_thead = T)
```
